New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems\tnoteref{t1}

### 2020-07-19 paper/article.tex
finsh some corrections

\section*{Abstract}
			%% Text of abstract
			Planar Maximum Covering Location by Ellipses is an optimization problem where one wants to place fixed shape ellipses on the plane to cover demand points
			maximizing a function depending on the value of covered points.
			We propose new exact algorithms for two versions of this problem, one where the ellipses have to be parallel to the coordinate axis, and another where they can be freely rotated. 
			Besides finding optimal solutions for previously published instances, including the ones where no optimal solution was known, both algorithms proposed by us were able to obtain optimal solutions for some new larger instances 	with up to seven hundred demand points and five ellipses.
\subsection*{Keywords}
			Combinatorial optimization, planar maximal covering location problem, planar covering by ellipses, exact algorithms.
			%% keywords here, in the form: keyword \sep keyword

@@

\clearpage
%\section*{References}
	%% New version of the num-names style
	%\bibliographystyle{natdin}
	\bibliography{../references}

>>>>

\section*{Abstract}
			%% Text of abstract

			{\color{Red}
		Planar Maximum Covering Location by Ellipses is an optimization problem where one wants to choose the location of ellipses given their major and minor axis to cover demand points, maximizing a function depending on the value of covered points.	
		}We propose new exact algorithms for two versions of this problem, one where the ellipses have to be parallel to the coordinate axis, and another where they can be freely rotated. 
			Besides finding optimal solutions for previously published instances, including the ones where no optimal solution was known, both algorithms proposed by us were able to obtain optimal solutions for some new larger instances 	with up to seven hundred demand points and five ellipses.
\subsection*{Keywords}
			Combinatorial optimization, planar maximal covering location problem, planar covering by ellipses, exact algorithms.
			%% keywords here, in the form: keyword \sep keyword

@@

\clearpage
%\section*{References}
	%% New version of the num-names style
	%\bibliographystyle{natdin}
	\bibliography{../defesa/references}

### 2020-07-19 paper/conclusion.tex
finsh some corrections

{\color{Green}
	Finally, we leave some additional suggestions for future works on this subject. We believe that fixing only the area of each ellipse, instead of its shape, can be an interesting extension of MCE and MCER; having only one additional decision variable --the major or minor axis-- might still allow a similar model to be employed, even though, extensive work would be necessary to adapt, somehow, the theory developed for this version, especially, of MCER.
We also believe that investigating coverage of points by ellipsoids in higher dimensions can be a great subject of future studies taking this work as the starting point; 
coming up with a general theoretical result for a $d$-dimension MCER, allowing it to be transformed into a combinatorial optimization problem like it was done here for the two-dimensional case, seems to be very challenging, and even though there might be no practical applications for this generalization, it is still very interesting from the theoretical perspective.
}

>>>>

{\color{Green}
	Finally, we leave some additional suggestions for future works on this subject. We believe that fixing only the area of each ellipse, instead of its shape, can be an interesting extension of MCE and MCER; having only one additional decision variable --the major or minor axis-- might still allow a similar model to be employed, even though, extensive work would be necessary to adapt, somehow, the theory developed for this version, especially, of MCER.
We also believe that investigating coverage of points by ellipsoids in higher dimensions can be a great subject of future studies taking this work as the starting point; 
coming up with a general theoretical result for a $d$-dimension MCER, allowing it to be transformed into a combinatorial optimization problem like it was done here for the two-dimensional case, seems to be very challenging, and even though there might be no practical applications for this generalization, it is still very interesting from the theoretical perspective. 
{\color{Red}Lastly, as it has been pointed out, the critical parameter of both algorithms developed in this paper is the number of ellipses, we think that trading-off being able to run with large demand sets can be the basis for future work on an alternative algorithm that can obtain optimal solutions for instances with larger sets of ellipses.}
}

### 2020-07-19 paper/cover.tex
finsh some corrections

\documentclass{article}

@@

\RequirePackage{algorithm, algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\newcommand{\algorithmautorefname}{Algorithm}
\newcommand{\definitionautorefname}{Definition}
\newcommand{\thmautorefname}{Theorem}
\newcommand{\prpautorefname}{Proposition}
\newcommand{\lemmaautorefname}{Lemma}
\newcommand{\lemautorefname}{Lemma}
\newcommand{\sigla}[2]{#2 (#1)}
\newcommand{\citeonline}[1]{\cite{#1}}

\begin{document}
		\title{Cover Letter}
		\maketitle

		Dear Editor, we herewith submit the manuscript entitled New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems addressing two not-vastly-explored problems on which we could only find two published papers, with the most recent one being from seven years ago.

@@

		%\section*{References}
		%% New version of the num-names style
		%\bibliographystyle{elsarticle-num}
		%\bibliography{../references}

>>>>

\documentclass[letterpaper]{letter}

@@

\RequirePackage{algorithm, algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\newcommand{\algorithmautorefname}{Algorithm}
\newcommand{\definitionautorefname}{Definition}
\newcommand{\thmautorefname}{Theorem}
\newcommand{\prpautorefname}{Proposition}
\newcommand{\lemmaautorefname}{Lemma}
\newcommand{\lemautorefname}{Lemma}
\newcommand{\sigla}[2]{#2 (#1)}
\newcommand{\citeonline}[1]{\cite{#1}}
\signature{Danilo Tedeschi}

\begin{document}

		%\title{Cover Letter}
		%\maketitle

		\begin{letter}{}

			\opening{Dear Prof. Roman Slowinski\\Coordinating Editor of EJOR}

		 We herewith submit the manuscript entitled New Exact Algorithms for Planar Maximum Covering Location by Ellipses Problems addressing two not-vastly-explored problems on which we could only find two published papers, with the most recent one being from seven years ago.

@@

		\closing{On behalf of the authors and with our best regards,}
			\end{letter}
		%\section*{References}
		%% New version of the num-names style
		%\bibliographystyle{elsarticle-num}
		%\bibliography{../references}

### 2020-07-19 paper/definition.tex
finsh some corrections

Let $\E=\{E_1, \dots, E_m\}$ be a list of functions representing the coverage area of each facility, with $E_j \colon \R^2 \to \R^2$ for MCE, and $E_j \colon \R^2\times [0, \pi)\to \R^2$. Let $||\cdot||_{a,b, \theta} \colon \R^2 \to \R_{\ge0}$ denote the elliptical norm given by
\begin{equation*}
||x||_{a,b, \theta}=\left|\left|
\left(\begin{array}{rr}
\cos{\theta} & \sin{\theta}\\
\sin{\theta} & -\cos{\theta}
\end{array}
\right)
\left(\begin{array}{cc}
1/a & 0\\
0 & 1/b
\end{array}\right) x \right|\right|_2,
\end{equation*}
then, for MCE we define $E_j(q)=\{p \in \R^2 \colon ||p-q||_{a_j,b_j,0} \le 1\}$; and for MCER we define $E_j(q, \theta)=\{p \in \R^2 \colon ||p-q||_{a_j,b_j, \theta} \le 1\}$.

@@

%%% esse paragrafo ainda ta estranho.
We use the notation $\partial$ to denote the boundary operator. For example, let $E \colon \R^2\to\R^2$ be the coverage region of an axis-parallel ellipse, then let $q\in\R^2$, $\partial E(q)$ describes an axis-parallel ellipse centered at $q$. If $E$ has shape parameters $(a, b)$, then $\partial E(q) = \{p \in \R^2\colon ||p-q||_{a,b,0} = 1\}$.

>>>>

Let $\E=\{E_1, \dots, E_m\}$ be a list of functions representing the coverage area of each facility, with $E_j \colon \R^2 \to {\color{blue}\mathcal{P}(\R^2)}$ for MCE, and $E_j \colon \R^2\times [0, \pi)\to {\color{blue}\mathcal{P}(\R^2)}$. Let $||\cdot||_{a,b, \theta} \colon \R^2 \to \R_{\ge0}$ denote the elliptical norm given by
\begin{equation*}
||x||_{a,b, \theta}=\left|\left|
\left(\begin{array}{rr}
\cos{\theta} & \sin{\theta}\\
\sin{\theta} & -\cos{\theta}
\end{array}
\right)
\left(\begin{array}{cc}
1/a & 0\\
0 & 1/b
\end{array}\right) x \right|\right|_2,
\end{equation*}
then, for MCE we define $E_j(q)=\{p \in \R^2 \colon ||p-q||_{a_j,b_j,0} \le 1\}$; and for MCER we define $E_j(q, \theta)=\{p \in \R^2 \colon ||p-q||_{a_j,b_j, \theta} \le 1\}$.

@@

%%% esse paragrafo ainda ta estranho.
We use the notation $\partial$ to denote the boundary operator. For example, let $E \colon \R^2\to{\color{blue} \mathcal{P}(\R^2)}$ be the coverage region of an axis-parallel ellipse, then let $q\in\R^2$, $\partial E(q)$ describes an axis-parallel ellipse centered at $q$. If $E$ has shape parameters $(a, b)$, then $\partial E(q) = \{p \in \R^2\colon ||p-q||_{a,b,0} = 1\}$.

### 2020-07-19 paper/e3p.tex
finsh some corrections

Given the shape parameters of an ellipse $(a, b) \in \R^2_{>0}$, $a > b$, and three points $u, v, w \in \R^2$, let $E\colon \R^2\times [0, \pi)\to\R^2$ be the coverage region of an ellipse with shape parameters $(a, b)$, we refer to the problem of obtaining $(q, \theta) \in \R^2\times [0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$ as Ellipse by Three Points Problem (E3P).
Because of its application here in our work, we are only interested in a method that can obtain every solution of E3P.

@@

Applying a rotation of $-\theta$ to the coordinate system makes the ellipse in the original solution become axis-parallel.
Then, that ellipse can be transformed into a circle of radius $b$ by squeezing the $x$-axis by $b/a$. This two-step transformation can be written as a function $\varphi\colon \R^2 \to \R^2$ defined as

\begin{equation*}%\label{eq:trpnts}
\varphi(p, \theta)=\left[\begin{array}{cc}
\frac{b}{a}&0\\
0&1
\end{array}\right]
\left[\begin{array}{cc}
\cos{\theta}&\sin{\theta}\\
-\sin{\theta}&\cos{\theta}
\end{array}\right]\left[\begin{array}{c}
p_x\\
p_y
\end{array}\right].
\end{equation*}

An example of this transformation can be seen in \autoref{fig:circumscribed-circle}. As $\varphi^{-1}$ is well-defined, instead of solving E3P, we can work with the univariate problem of determining an angle of rotation $\theta \in [0, \pi)$ that makes the triangle with vertices $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$ be circumscribed in a circle of radius $b$. To make the notation less cluttered, we denote by $\Lambda(\theta)$ the triangle with vertices $\varphi(u, \theta), \varphi(v, \theta), \varphi(w, \theta)$.

@@

As circles are uniquely defined by three non-collinear points, the circumcircle of $\Lambda(\theta)$ is unique, and its radius and center can be determined analytically \cite{weisstein}.
Let $|\Lambda(\theta)|$ denote the area of $\Lambda(\theta)$, using the formula from \cite[p.~189]{johnson1960} for the radius of a circumcircle of a triangle, and imposing that radius to be equal $b$, we define a function $\xi \colon [0, \pi) \to \R$ as
\begin{equation}\label{eq:xi}
\xi(\theta) = 16b^2|\Lambda(\theta)|^2 - \norm{\varphi(v, \theta)}^2\norm{\varphi(w, \theta)}^2\norm{\varphi(v, \theta)-\varphi(w, \theta)}^2,
\end{equation}
whose roots are angles of rotation which determine solutions of E3P through the inverse transformation $\varphi^{-1}$.
From a root $\hat{\theta}$ of $\xi$, let $\hat{q}$ be the center of the circumcircle of $\Lambda(\hat{\theta})$, the solution $(\varphi^{-1}(\hat{q}), \hat{\theta})$ of E3P is obtained.

@@

\begin{proof}
	The first thing to notice is that $\xi$ is a real trigonometric polynomial of degree $6$. 
	Its term of highest degree is the multiplication of the norms $\norm{\varphi(v, \theta)}^2\norm{\varphi(w, \theta)}^2\norm{\varphi(v, \theta)-\varphi(w, \theta)}^2$. In \cite[p.~150]{powell}, where a definition of real trigonometric polynomial is also given, it is stated that a $n$-degree real trigonometric polynomial can have up to $2n$ roots in $[0, 2\pi)$. Therefore, E3P has at most $12$ solutions in $[0, 2\pi]$.
	Half of these solutions, though, are duplicated as ellipses are symmetric to their axis.
\end{proof}

@@

In \cite[p.~195]{horn}, a theorem is presented stating that for every univariate polynomial of degree $n$, there exists a companion matrix, which is a $n\times n$ matrix, such that its eigenvalues are the zeros of that polynomial. Finding every eigenvalue of a matrix can be done using the QR algorithm, which runs in $\bigO(n^3)$ and uses $\bigO(n^2)$ memory (a very complete introduction to it can be found in \cite{watkins:2008}). For example, for a degree-$4$ polynomial $\sum_{k=0}^4 a_k x^4$, a possible companion matrix is given by

@@

The experiment considered instances of E3P where the three points are the vertices of an ellipse rotated by $\theta\in[0, \pi)$. Such instances only have one solution, and therefore, roots with multiplicity greater than one are expected.
For each value of $K$, we ran the algorithm for $100$ instances generated randomly by sampling $\theta$ according to a uniform distribution. For each instance, we took the root $\hat{z}$ which produced the closest solution to the known one. Then, for each $K$, as it can be seen in \autoref{fig:e3p_known_sols2}, we considered the maximum and the average distance to the unit circle $|1-|\hat{z}||$; and, as it presented in \autoref{fig:e3p_known_sols1}, the maximum and average error $|f(\hat{z})|$.

>>>>

Given the shape parameters of an ellipse $(a, b) \in \R^2_{>0}$, $a > b$, and three points $u, v, w \in \R^2$, let $E\colon \R^2\times [0, \pi)\to{\color{blue}\mathcal{P}(\R^2)}$ be the coverage region of an ellipse with shape parameters $(a, b)$, we refer to the problem of obtaining $(q, \theta) \in \R^2\times [0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$ as Ellipse by Three Points Problem (E3P).
Because of its application here in our work, we are only interested in a method that can obtain every solution of E3P.

@@

Applying a rotation of $-\theta$ to the coordinate system makes the ellipse in the original solution become axis-parallel.
Then, that ellipse can be transformed into a circle of radius $b$ by squeezing the $x$-axis by $b/a$. This two-step transformation can be written as a function ${\color{blue}\varphi_\theta\colon \R^2 \to \R^2}$ defined as

\color{blue}
\begin{equation*}%\label{eq:trpnts}
\varphi_\theta(p)=\left[\begin{array}{cc}
\frac{b}{a}&0\\
0&1
\end{array}\right]
\left[\begin{array}{cc}
\cos{\theta}&\sin{\theta}\\
-\sin{\theta}&\cos{\theta}
\end{array}\right]\left[\begin{array}{c}
p_x\\
p_y
\end{array}\right].
\end{equation*}
\color{black}

An example of this transformation can be seen in \autoref{fig:circumscribed-circle}. As {\color{blue} $\varphi_\theta^{-1}$} is well-defined, instead of solving E3P, we can work with the univariate problem of determining an angle of rotation $\theta \in [0, \pi)$ that makes the triangle with vertices {\color{blue}$\varphi_\theta(u), \varphi_\theta(v), \varphi_\theta(w)$} be circumscribed in a circle of radius $b$. To make the notation less cluttered, we denote by $\Lambda(\theta)$ the triangle with vertices {\color{blue}$\varphi_\theta(u), \varphi_\theta(v), \varphi_\theta(w)$}.

@@

As circles are uniquely defined by three non-collinear points, the circumcircle of $\Lambda(\theta)$ is unique, and its radius and center can be determined analytically \cite{weisstein}.
Let $|\Lambda(\theta)|$ denote the area of $\Lambda(\theta)$, using the formula from \cite[p.~189]{johnson1960} for the radius of a circumcircle of a triangle, and imposing that radius to be equal $b$, we define a function $\xi \colon [0, \pi) \to \R$ as
\begin{equation}\label{eq:xi}
\xi(\theta) = 16b^2|\Lambda(\theta)|^2 - \norm{{\color{blue}\varphi_\theta(v)}}^2\norm{{\color{blue}\varphi_\theta(w)}}^2\norm{{\color{blue}\varphi_\theta(v)}-{\color{blue}\varphi_\theta(w)}}^2,
\end{equation}
whose roots are angles of rotation which determine solutions of E3P through the inverse transformation {\color{blue}$\varphi_\theta^{-1}$}.
From a root $\hat{\theta}$ of $\xi$, let $\hat{q}$ be the center of the circumcircle of $\Lambda(\hat{\theta})$, the solution $({\color{blue}\varphi_{\hat{\theta}}^{-1}}(\hat{q}), \hat{\theta})$ of E3P is obtained.

@@

\begin{proof}
	The first thing to notice is that $\xi$ is a real trigonometric polynomial of degree $6$. 
	Its term of highest degree is the multiplication of the norms $\norm{{\color{blue}\varphi_\theta(v)}}^2\norm{{\color{blue}\varphi_\theta(w)}}^2\norm{{\color{blue}\varphi_\theta(v)}-{\color{blue}\varphi_\theta(w)}}^2$. In \cite[p.~150]{powell}, where a definition of real trigonometric polynomial is also given, it is stated that a $n$-degree real trigonometric polynomial can have up to $2n$ roots in $[0, 2\pi)$. Therefore, E3P has at most $12$ solutions in $[0, 2\pi]$.
	Half of these solutions, though, are duplicated as ellipses are symmetric to their axis.
\end{proof}

@@

In \cite[p.~195]{horn}, a theorem is presented stating that for every univariate polynomial of degree $n$, there exists a companion matrix, which is a $n\times n$ matrix, such that its eigenvalues are the zeros of that polynomial. Finding every eigenvalue of a matrix can be done using the QR algorithm, which runs in $\bigO(n^3)$ and uses $\bigO(n^2)$ memory (a very complete introduction to it can be found in \cite{watkins:2008}). For example, for a {\color{blue} $4$-degree} polynomial $\sum_{k=0}^4 a_k x^4$, a possible companion matrix is given by

@@

The experiment considered instances of E3P where the three points are vertices of an ellipse rotated by $\theta\in[0, \pi)$. Such instances only have one solution, and therefore, roots with multiplicity greater than one are expected.
For each value of $K$, we ran the algorithm for $100$ instances generated randomly by sampling $\theta$ according to a uniform distribution. For each instance, we took the root $\hat{z}$ which produced the closest solution to the known one. Then, for each $K$, as it can be seen in \autoref{fig:e3p_known_sols2}, we considered the maximum and the average distance to the unit circle $|1-|\hat{z}||$; and, as it presented in \autoref{fig:e3p_known_sols1}, the maximum and average error $|f(\hat{z})|$.

### 2020-07-19 paper/implementation.tex
finsh some corrections

In the algorithm to obtain every solution of E3P described in \autoref{section:e3p}, we assumed that a procedure which returns every eigenvalue of a given complex matrix was available. In practice, we used the famous linear algebra package LAPACK (see \cite{lapack} for more details).
Even though LAPACK is a library for the FORTRAN programming language, its routines can be made available in a C/C++ environment by simply adding the \textit{-llapack} linking flag to the compilation. The only remarks, though, are that FORTRAN represents matrices in a column-major fashion, and receives parameters only by reference. Therefore, matrices must be transposed before being passed to a routine, and every parameter must receive a pointer to a variable containing its value.

@@

Back in \autoref{section:e3p}, we were faced with the problem of writing function $\xi$ defined in \autoref{eq:xi} as a complex polynomial in the new variable $z=e^{i\theta}$. We suggested that symbolic computation should be used for this task, as the expressions for that polynomial's coefficients become very long, and doing that by hand is, to say the least, a very tedious work.
Symbolic computation is a vast topic, which deals with the problem of solving or manipulating mathematical expressions computationally. 
In practice, we utilized an external library for Python called SymPy (see \cite{sympy} for more information).
This tool can create expressions using arithmetic operators on predefined symbols, numbers, and other expressions. It can also convert expressions into polynomials in the power format, and output them directly into C code. Using these features, we wrote $\xi(\theta)(e^{i\theta})^6$ as a polynomial by replacing the sine and cosine functions by the identities $\cos\theta=(z+z^{-1})/2$ and $\sin\theta=(z+z^{-1})/(2i)$.

>>>>

In the algorithm to obtain every solution of E3P described in Section~\ref{section:e3p}, we assumed that a procedure which returns every eigenvalue of a given complex matrix was available. In practice, we used the famous linear algebra package LAPACK (see \cite{lapack} for more details).
Even though LAPACK is a library for the FORTRAN programming language, its routines can be made available in a C/C++ environment by simply adding the \textit{-llapack} linking flag to the compilation. The only remarks, though, are that FORTRAN represents matrices in a column-major fashion, and receives parameters only by reference. Therefore, matrices must be transposed before being passed to a routine, and every parameter must receive a pointer to a variable containing its value.

@@

Back in Section~\ref{section:e3p}, we were faced with the problem of writing function $\xi$ defined in \autoref{eq:xi} as a complex polynomial in the new variable $z=e^{i\theta}$. We suggested that symbolic computation should be used for this task, as the expressions for that polynomial's coefficients become very long, and doing that by hand is, to say the least, a very tedious work.
Symbolic computation is a vast topic, which deals with the problem of solving or manipulating mathematical expressions computationally. 
In practice, we utilized an external library for Python called SymPy (see \cite{sympy} for more information).
This tool can create expressions using arithmetic operators on predefined symbols, numbers, and other expressions. It can also convert expressions into polynomials in the power format, and output them directly into C code. Using these features, we wrote $\xi(\theta)(e^{i\theta})^6$ as a polynomial by replacing the sine and cosine functions by the identities $\cos\theta=(z+z^{-1})/2$ and $\sin\theta=(z+z^{-1})/(2i)$.

### 2020-07-19 paper/introduction.tex
finsh some corrections

PMCLP can be seen as a class of problems, as, in general, facilities can have their coverage defined by any norm function, and the demand set, although initially defined as points, could have a more generic definition; in \cite{bansal}, for example, they are defined as rectangles.
In \cite{church:1984}, a method was proposed for the version of PMCLP, where the facilities have Euclidean norm coverage. This method consisted of obtaining a discrete set of solutions for each facility, which was proved to contain at least one optimal solution, and then using the model developed for MCLP in \cite{church:1974} to determine an optimal solution.

@@

We study two versions of PMCLP with elliptical coverage facilities in this work. For both of them, each ellipse is defined to have a fixed shape and an undefined location, which is part of the solution.
In the first version, introduced in \cite{canbolat}, all the ellipses are restricted to be axis-parallel, while in the second version, introduced in \cite{andreta}, this constraint is dropped, and all the ellipses can be freely rotated.
The first version will be referred to as \sigla{MCE}{Planar Maximum Covering Location by Ellipses Problem} and the second one as  \sigla{MCER}{Planar Maximum Covering Location by Ellipses with Rotation Problem}.

>>>>

{\color{Red}PMCLP can be seen as a class of problems, as, in general, facilities can have their coverage defined by any norm function, and the demand set, although initially defined as points, could have a more generic definition; in \cite{bansal}, for example, the demand set is defined as a set of rectangles; and in \cite{younies}, a version of PMCLP where coverage is determined using block norms is studied. For a more comprehensive review on PMCLP and MCLP, please see \cite{murray}.}

{\color{Red}In our work, because of the similarities with the problems studied by us, we are particularly interested in the Euclidean PMCLP defined with coverage being determined by the Euclidean norm. In \cite{church:1984}, a method for this version of PMCLP was developed following the demonstration of a theorem, which showed that a finite set of locations could be constructed to contain at least one optimal solution transforming PMCLP into a combinatorial optimization problem.}

@@

We study two versions of PMCLP with elliptical coverage facilities in this work. For both of them, each ellipse is defined to have {\color{Red}fixed major and minor axis} and an undefined location, which is part of the solution.
In the first version, introduced in \cite{canbolat}, all the ellipses are restricted to be axis-parallel, while in the second version, introduced in \cite{andreta}, this constraint is dropped, and all the ellipses can be freely rotated.
The first version will be referred to as \sigla{MCE}{Planar Maximum Covering Location by Ellipses Problem} and the second one as  \sigla{MCER}{Planar Maximum Covering Location by Ellipses with Rotation Problem}.

### 2020-07-19 paper/prunning.tex
finsh some corrections

Suppose that the first $k$ ellipses are fixed at locations $(q_1,\dots, q_k)$, and that we have an lower-bound $L$ for the value of an optimal solution. Let $Z_k=\Pp\setminus \cup_{j=1}^k E_j(q_j)$ be the points not covered by the first $k$ ellipses, then we can use \autoref{eq:upper-1} to verify if we can skip every solution where the first $k$ ellipses are fixed at  $(q_1,\dots, q_k)$ or not.
If
\begin{equation}\label{eq:upper}
w\left(\bigcup_{j=1}^{k} \Pp \cap E_j(q_j)\right)+
\sum_{j=k+1}^m \max_{q_j} w(Z_j \cap E_j(q_j)) \le L,
\end{equation}
then, any solution with the first $k$ ellipses fixed at $(q_1,\dots, q_k)$ will have value less than or equal to the value of an optimal solution, therefore, we can cut the backtracking tree there. In practice, we can use the value of the best solution found at the moment as the lower-bound $L$.

>>>>

Suppose that the first $k$ ellipses are fixed at locations $(q_1,\dots, q_k)$, and that we have a lower-bound $L$ for the value of an optimal solution. Let $Z_k=\Pp\setminus \cup_{j=1}^k E_j(q_j)$ be the points not covered by the first $k$ ellipses, then we can use \autoref{eq:upper-1} to verify if we can skip every solution where the first $k$ ellipses are fixed at  $(q_1,\dots, q_k)$ or not.
If
\begin{equation}\label{eq:upper}
w\left(\bigcup_{j=1}^{k} \Pp \cap E_j(q_j)\right)+
\sum_{j=k+1}^m \max_{q_j} w(Z_j \cap E_j(q_j)) \le L,
\end{equation}
then, any solution with the first $k$ ellipses fixed at $(q_1,\dots, q_k)$ will have value less than or equal to the value of an optimal solution, therefore, we can cut the backtracking tree there. In practice, we can use the value of the best solution found at the moment as the lower-bound $L$.
